Hurricane Evacuation Strategies for the State of Mississippi

### 2015-11-16 manuscript.tex
Added original prompt

\section{Stochastic Model of Landfall-Avodiant Evacuations}
\label{sec:stochastic}
  \subsection{Model Description}
    In this model, instead of giving citizens particular evacuation plan, we give them a simple rule.
  \subsection{Parameter Values and Justification}
  \subsection{Results}
  \begin{figure}
    \center
    \begin{subfigure}[b]{0.5\textwidth}
      \center
      \includegraphics[width=\linewidth]{figures/pred_hancock-crop.pdf}
      \caption{Predicted Evacuation for Landfall in Hancock County}
    \end{subfigure}~
    \begin{subfigure}[b]{0.5\textwidth}
      \center
      \includegraphics[width=\linewidth]{figures/pred_jackson-crop.pdf}
      \caption{Predicted Evacuation for Landfall in Jackson County}
    \end{subfigure}
    \caption{}
  \end{figure}
  \subsection{Strengths and Weaknesses}

>>>>

\section{Stochastic Model of Landfall-Avodiant Evacuations}
\label{sec:stochastic}
  \subsection{Model Description}
    \par In this model, instead of giving citizens particular evacuation plan, we give them a simple rule: flee directly away from the hurricane landfall if possible, else move North or North-West. Assuming that Mississippi has a statewide
  \subsection{Parameter Values and Justification}

  \subsection{Results}

    \begin{figure}
      \center
      \begin{subfigure}[b]{0.5\textwidth}
        \center
        \includegraphics[width=\linewidth]{figures/pred_hancock-crop.pdf}
        \caption{Predicted Evacuation for Landfall in Hancock County}
      \end{subfigure}~
      \begin{subfigure}[b]{0.5\textwidth}
        \center
        \includegraphics[width=\linewidth]{figures/pred_jackson-crop.pdf}
        \caption{Predicted Evacuation for Landfall in Jackson County}
      \end{subfigure}
      \caption{}
    \end{figure}
  \subsection{Strengths and Weaknesses}
